Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-05-28 snapshot_system/impl.tex
add architecture

\section{Deletion}
In a mature VM cluster, snapshot deletions are as frequent as snapshot creations.
Our system adopts lazy delete strategy so that all snapshot deletions are scheduled
in the backup time window at midnight. 
Therefore, snapshot deletions must be fast enough to fit in time window and
efficient enough to satisfy our resource constraints.
However, there is no simple solution can achieve these goals with high reliability.
In Aliyun's cloud, we use a {\em fuzzy deletion} method to trade deletion accuracy for
speed and resource usage. This method tolerates a tiny percentage of storage leakage
to make the deletion operation faster and efficient by an order of magnitude,
yet we still adopt an slow but accurate deletion method to fix such leakage in the long-term.
Our hybrid deletion strategy, using fuzzy deletion regularly and accurate deletion periodically,
accomplishs our speed, resource usage and relibility goals very well.

% \subsection{Challenges}
% Contrary to a traditional backup system, a dedupe system shares data among files by default. 
% Reference management is necessary to keep track of chunk usage and reclaim freed space. 
% In addition to scalability and speed, reliability is another challenge for reference management. 
% If a chunk gets freed while it is still referenced by snapshots, data loss occurs and files cannot be restored. 
% On the other hand, if a chunk is referenced when it is actually no longer in use, it causes storage leakage.

% Reference counting, while being simple, suffers from low reliability especially in our distributed environment, 
% because it is vulnerable to lost or repeated updates: when errors occur some chunks maybe updated and some may not. 
% Complicated transaction rollback logic is required to make reference counts consistent. Moreover, 
% there is almost no way to verify if the reference count is correct or not in a large dynamic system. 
% In real deployments, where data integrity and recoverability directly affect product reputation, simple reference counting is unsatisfactory.

% Mark-and-sweep is generally a better solution. During the mark phase, all snapshot recipes are traversed so as to mark the used chunks. 
% In the sweep phase all chunks are swept and unmarked chunks are reclaimed. 
% This approach is very resilient to errors: at any time the process can simply be restarted with no negative side effects. 
% Scalability, however, is an issue. {\em needs to explain its resource usage}

\subsection{Approximate Deletion}
We design approximate deletion to fast identify unused data in the append store.
Instead of scanning the whold append store, it uses a bloom filter to check 
if a data are still referenced by living snapshots. However, there is a small false-positive probility which
would indetify unused data as in use, i.e., storage leakage.
The following steps would take place during an approximate deletion:

@@

\subsection{Accurate Deletion}
Our accurate deletion uses mark-and-sweep to find all the unused chunks in a VM's append store.
The following steps would take place during an accurate deletion:

@@

\subsection{Discussion}

>>>>

\section{Implementation}
\subsection{Snapshot Backup}
\subsection{Snapshot Read}
\subsection{Snapshot Deletion}
In a mature VM cluster, snapshot deletions are as frequent as snapshot creations.
Our system adopts lazy delete strategy so that all snapshot deletions are scheduled
in the backup time window at midnight. 
Therefore, snapshot deletions must be fast enough to fit in time window and
efficient enough to satisfy our resource constraints.
However, there is no simple solution can achieve these goals with high reliability.
In Aliyun's cloud, we use a {\em fuzzy deletion} method to trade deletion accuracy for
speed and resource usage. This method tolerates a tiny percentage of storage leakage
to make the deletion operation faster and efficient by an order of magnitude,
yet we still adopt an slow but accurate deletion method to fix such leakage in the long-term.
Our hybrid deletion strategy, using fuzzy deletion regularly and accurate deletion periodically,
accomplishs our speed, resource usage and relibility goals very well.

{\bf Approximate Deletion}
We design approximate deletion to fast identify unused data in the append store.
Instead of scanning the whold append store, it uses a bloom filter to check 
if a data are still referenced by living snapshots. However, there is a small false-positive probility which
would indetify unused data as in use, i.e., storage leakage.
The following steps would take place during an approximate deletion:

@@

{\bf Append Store Cleanup}
Our accurate deletion uses mark-and-sweep to find all the unused chunks in a VM's append store.
The following steps would take place during an accurate deletion:

@@
